Object naming is context dependent - A case study on testing linguistic hypotheses on real-world image corpora

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
Adds practical requirements for datasets

In practical terms, the prerequisite for Requirements~(2) and~(3) is, given an image, the information on \textbf{R1: the most specific category} of \textbf{each object} which is depicted in the image. 
A taxonomy, such as WordNet \cite{fellbaum1998wordnet}, could then be queried with these categories to retrieve their individual lexical candidates arranged by their taxonomic relations. \\
Furthermore, the information on the \textbf{R2: entry-level category} of an object could be used as a pivot to taxonomically group its lexical candidates.

With respect to linguistic data-driven experiments, the range of linguistic phenomena under study (see, e.g.,~Section~\ref{sec:object_naming} for phenomena in object naming) need to be observable in the data in order to study the interaction of their underlying factors. 
Hence, a further practical requirement is that the data, first, captures ideally all possible combinations of the factor values across all factors\footnote{For example, data that contains only images where target and distractor objects do not share any lexical candidates would not be appropriate}, and second, that it has been naturally produced in that speakers were not constraint in their choice of a name by external factors. 
We summarize this requirement by the term \textbf{R3: unconstraint}. 
Note that this requirement XXX \cs{@Sina ref to bias and paper you mentioned?}.
\section{Resources: What Do We Have?}
\label{sec:resources}
\input{resources}

>>>>

\cs{Should the following be here or at the beginning of Sect. 4?}
\cs{We could also call below requirements "Desiderata"}
In practical terms, the prerequisite for Requirements~(2) and~(3) is, given an image, the information on \textbf{R1: the most specific category} of \textbf{each object} which is depicted in the image. 
A taxonomy, such as WordNet \cite{fellbaum1998wordnet}, could then be queried with these categories to retrieve their individual lexical candidates arranged by their taxonomic relations. \\
Furthermore, the information on the \textbf{R2: entry-level category} of an object could be used as a pivot to taxonomically group its lexical candidates.

With respect to linguistic data-driven experiments, the range of linguistic phenomena under study (see, e.g.,~Section~\ref{sec:object_naming} for phenomena in object naming) need to be observable in the data in order to study the interaction of their underlying factors. 
Hence, a further practical requirement is that the data, first, captures ideally all possible combinations of the factor values across all factors\footnote{For example, data that contains only images where target and distractor objects do not share any lexical candidates would not be appropriate}, and second, that it has been naturally produced in that speakers were not constraint in their choice of a name by external factors. 
We summarize this requirement by the term \textbf{R3: unconstraint}. 
Note that this requirement XXX \cs{@Sina ref to bias and paper you mentioned?}.

\section{Resources: What Do We Have?}
\label{sec:resources}
\input{resources}
